Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidic System

### 2022-12-10 paper-kelompok/main.tex
Minor typo change

\section{Results and Discussion}
\subsection{Accuracy}
Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b7}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
The resulting liquid was then dropped between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.

>>>>

\section{Results and Discussion}
\subsection{Accuracy}
Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b7}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml.
The resulting liquid was then dropped between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.
